---
title: 'Vermont Priority Program Question Results'
author: "Samuel McQuillin"
date: "May 16, 2016"
output: pdf_document
digits: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
```
```{r, echo=FALSE}
#Dr. McQuillins UH Office Source
#setwd("C:/R/nmrcsurvey")
#Dr. McQuillin's Home Computer
setwd("C:/Users/Sam/R/nmrcsurvey")
source("mergeclean.R")
statefun("Vermont")
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

stdfmcom<-stdfm[ which(stdfm$STAT=="Complete"),]
library(ggplot2)
stdfmcom$MODELp<-factor(stdfmcom$MODELp,
                  levels=c(1,2,3,4,5,6,7),
                  labels=c("1-to-1",
                  "Group",
                  "Blended",
                  "Team","Electronic","X-age peer",
                  "Other"))


stdfmcom$FREQpQ4<-factor(stdfmcom$FREQpQ4,
                  levels=c(1,2,3,4,5),
                  labels=c("Less than 25%",
                  "25-50%",
                  "51-75%",
                  "76-90%",
                  "More than 90%"))

stdfmcom$STAFFpQ6<-factor(stdfmcom$STAFFpQ6,
                  levels=c(1,2,3),
                  labels=c("Increase",
                  "Stay the same",
                  "Decrease"))

stdfmcom$YOUTHINCpQ1<-factor(stdfmcom$YOUTHINCpQ1,
                  levels=c(1,2,3),
                  labels=c("Increase",
                  "Stay the same",
                  "Decrease"))


stdfmcom$BUDGpQ2<-factor(stdfmcom$BUDGpQ2,
                  levels=c(1,2,3,4),
                  labels=c("Increased",
                  "Stayed roughly the same",
                  "Fluctuated",
                  "Decreased"))

stdfmcom$BUDGpQ4<-factor(stdfmcom$BUDGpQ4,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))

stdfmcom$BUDGpQ5<-factor(stdfmcom$BUDGpQ5,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ6<-factor(stdfmcom$BUDGpQ6,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ7<-factor(stdfmcom$BUDGpQ7,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ8<-factor(stdfmcom$BUDGpQ8,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ9<-factor(stdfmcom$BUDGpQ9,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ10<-factor(stdfmcom$BUDGpQ10,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ11<-factor(stdfmcom$BUDGpQ11,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ12<-factor(stdfmcom$BUDGpQ12,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ13<-factor(stdfmcom$BUDGpQ13,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ14<-factor(stdfmcom$BUDGpQ14,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ15<-factor(stdfmcom$BUDGpQ15,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))
stdfmcom$BUDGpQ16<-factor(stdfmcom$BUDGpQ16,
                  levels=c(1,2,3,4,5,6),
                  labels=c("Under 10%",
                  "10-25%",
                  "26-50%",
                  "51-75%",
                  "76-90%",
                  "Over 90%"))


```


```{r, echo=FALSE}
bar <- ggplot(stdfmcom, aes(factor(MODELp)))
bar+geom_bar()+labs(title="Type of Mentoring Program",x="Type",y="Number of Programs Reporting")
```

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$MODELp)))
knitr::kable(k,col.names=c("Model","Proportion"),digits=2)
```

```{r, echo=FALSE}
bar <- ggplot(stdfmcom, aes(YEARSp))
bar+geom_bar()+labs(title="Number of years program has been active",x="Years",y="Frequency")
```

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$YEARSp)))
knitr::kable(k,col.names=c("Years","Proportion"),digits=2)
```

#Top four program focus by frequency and percent

 Focus                | Frequency     | Proportion
 -------------        | ------------- | ------------- |   
 Academic enrichment  | `r sum(stdfmcom$GOALSpQ1,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ1,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Career exploration   | `r sum(stdfmcom$GOALSpQ2,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ2,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Civic engagement     | `r sum(stdfmcom$GOALSpQ3,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ3,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)` 
 College access       | `r sum(stdfmcom$GOALSpQ4,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ4,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)` 
 Educational Attainment  | `r sum(stdfmcom$GOALSpQ5,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ5,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Family support  | `r sum(stdfmcom$GOALSpQ6,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ6,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 General youth development  | `r sum(stdfmcom$GOALSpQ7,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ7,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Identity development  | `r sum(stdfmcom$GOALSpQ8,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ8,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Juvenile justice/re-entry  | `r sum(stdfmcom$GOALSpQ9,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ9,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Leadership development  | `r sum(stdfmcom$GOALSpQ10,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ10,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Life skills/social skills  | `r sum(stdfmcom$GOALSpQ11,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ11,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Literacy  | `r sum(stdfmcom$GOALSpQ12,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ12,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Mental health and well-being  | `r sum(stdfmcom$GOALSpQ13,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ13,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Positive health behaviors  | `r sum(stdfmcom$GOALSpQ14,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ14,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Pregnancy prevention  | `r sum(stdfmcom$GOALSpQ15,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ15,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Providing a caring adult relationship  | `r sum(stdfmcom$GOALSpQ16,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ16,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Recreational activities  | `r sum(stdfmcom$GOALSpQ17,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ17,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Resiliency  | `r sum(stdfmcom$GOALSpQ18,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ18,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 STEM education   | `r sum(stdfmcom$GOALSpQ19,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ19,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Substance use/abuse  | `r sum(stdfmcom$GOALSpQ20,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ20,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Violence prevention   | `r sum(stdfmcom$GOALSpQ21,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ21,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Other  | `r sum(stdfmcom$GOALSpQ22,na.rm=TRUE)`  | `r round(sum(stdfmcom$GOALSpQ22,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`

#Percent of matches that met the minimum length


Overall average: %`r round(((mean(as.numeric(stdfmcom$FREQpQ4),na.rm=TRUE)-1)*25),digits=2)`

```{r, echo=FALSE}
bar <- ggplot(stdfmcom, aes(factor(FREQpQ4)))
bar+geom_bar()+labs(title="Percent matches that met minimum length",x="Percent",y="Number of Programs Reporting")
```

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$FREQpQ4)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

#Average length of matches

Median Duration: `r round(median(as.numeric(stdfmcom$FREQpQ15),na.rm=TRUE),digits=2)`  
Modal Duration: `r round(getmode(as.numeric(stdfmcom$FREQpQ15)),digits=2)`  
Mean Duration: `r round(mean(as.numeric(stdfmcom$FREQpQ15),na.rm=TRUE),digits=2)`  
NOTE: 2 Outliers exceed 150 months

```{r, echo=FALSE}
bar <- ggplot(stdfmcom, aes(FREQpQ15))
bar+geom_histogram(bins=10)+labs(title="Average Duration of Matches",x="Duration in Months",y="Frequency") +
  scale_x_continuous(breaks=seq(0,55,5),lim=c(0,55))
```

#Reasons for Matches Ending

 Reason                | Frequency     | Proportion
 -------------         | ------------- | ------------- |   
 Mentor change in life circumstances   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ5)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ5)))/dim(stdfmcom)[1],digits=2)`
 Mentee change in life circumstances   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ6)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ6)))/dim(stdfmcom)[1],digits=2)` 
 Mentor unfulfilled/unrealistic expectations   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ7)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ7)))/dim(stdfmcom)[1],digits=2)`
 Mentee unfulfilled/unrealistic expectations   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ8)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ8)))/dim(stdfmcom)[1],digits=2)`
 Mentor did not feel youth needed them   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ9)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ9)))/dim(stdfmcom)[1],digits=2)`
 Cultural differences   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ10)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ10)))/dim(stdfmcom)[1],digits=2)`
 Family interference/lack of support   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ11)))`  | `r round(as.numeric(!is.na(sum(stdfmcom$FREQpQ11)))/dim(stdfmcom)[1],digits=2)`
 Lack resources to provide match support   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ12)))`  | `r round(as.numeric(!is.na(sum(stdfmcom$FREQpQ12)))/dim(stdfmcom)[1],digits=2)`
 Unknown   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ13)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ13)))/dim(stdfmcom)[1],digits=2)`
 Other   | `r sum(as.numeric(!is.na(stdfmcom$FREQpQ14)))`  | `r round(sum(as.numeric(!is.na(stdfmcom$FREQpQ14)))/dim(stdfmcom)[1],digits=2)`


#Staffing Questions

Change in FTE Staff from previous year
```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$STAFFpQ6)))
knitr::kable(k,col.names=c("Change","Proportion"),digits=2)
```

```{r, echo=FALSE}
bar <- ggplot(stdfmcom, aes(STAFFpQ6))
bar+geom_bar()+labs(title="Staff Change from Previous Year",x="Change",y="Frequency")
```

#Budget Qestions
Budget stability over the past three years  

```{r, echo=FALSE}
bar <- ggplot(subset(stdfmcom,!is.na(BUDGpQ2)), aes(factor(BUDGpQ2)))
bar+geom_bar()+labs(title="Budget Stability over Past Three Years",x="Stability",y="Frequency")
```

```{r, echo=FALSE}
k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ2)))
knitr::kable(k,col.names=c("Change","Proportion"),digits=2)
```

#Budget Sources  

Federal government grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ4)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

State government grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ5)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

County or municipal grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ6)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

K-12 school/district/LEA/ESD grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ7)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Private foundation grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ8)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Community foundation grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ9)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

United Way grants  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ10)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Business or corporate donations  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ11)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Private philanthropy  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ12)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Individual donations  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ13)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Fundraising events  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ14)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Earned income/contracted income  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ15)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

Mentoring Parntership Support  

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$BUDGpQ16)))
knitr::kable(k,col.names=c("Percent Range","Proportion"),digits=2)
```

#Change in Youth Served

```{r, echo=FALSE}
bar <- ggplot(stdfmcom, aes(YOUTHINCpQ1))
bar+geom_bar()+labs(title="Stability in Number of Youth Served",x="Change",y="Frequency")
```

```{r, echo=FALSE}

k<-as.data.frame(prop.table(table(stdfmcom$YOUTHINCpQ1)))
knitr::kable(k,col.names=c("Change","Proportion"),digits=2)
```


 Reason               | Frequency     | Proportion
 -------------        | ------------- | ------------- |   
 Change in funding level   |     `r sum(stdfmcom$YOUTHINCpQ2,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ2,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Change in available staffing   |     `r sum(stdfmcom$YOUTHINCpQ3,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ3,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Change in community interest/demand   |     `r sum(stdfmcom$YOUTHINCpQ4,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ4,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Change in number of volunteers recruited   |     `r sum(stdfmcom$YOUTHINCpQ5,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ5,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Change in number of youth enrolling   |     `r sum(stdfmcom$YOUTHINCpQ6,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ6,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Change in program offerings   |     `r sum(stdfmcom$YOUTHINCpQ7,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ7,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`
 Other - Write In   |     `r sum(stdfmcom$YOUTHINCpQ8,na.rm=TRUE)`  | `r round(sum(stdfmcom$YOUTHINCpQ8,na.rm=TRUE)/dim(stdfmcom)[1],digits=2)`